### 2021-03-29 paper/ase21/abstract.tex
[ASE21] Bullet list for Introduction

  To alleviate this problem, we propose $\tool$, an ECMAScript Static Checker
  based on Refinement Types.  Our tool performs the following three steps for a
  given specification: 1) to convert abstract algorithms in the specification to
  untyped intermediate representation, 2) to extract type information of data
  structures used in the specification,  and 2) to perform type analysis with
  the extracted type information to detect specification errors.  Moreover, we
  use \textit{refinement types} over the extracted type information to reduce
  false alarms.  \inred{TODO: explanation of refinement types.} We evaluated
  $\tool$ with \inred{XXX different versions of ECMAScript in the official GitHub
  repository between 2018 June and 2021 March.} Among \inred{XXX} known
  specification errors, our tool detected \inred{XXX} errors with \inred{XXX}
  false alarms.  Moreover, $\tool$ detected \inred{X} new specification errors
  in the draft of next release of ECMAScript (ES12, 2021).
\end{abstract}

>>>>

  To alleviate this problem, we propose $\tool$, an ECMAScript Static Checker
  based on Refinement Types.  Our tool performs the following three steps for a
  given specification: 1) to convert abstract algorithms in the specification to
  untyped intermediate representation, 2) to extract type information of data
  structures used in the specification, and 3) to perform type analysis with the
  extracted type information to detect specification errors.  Moreover, we use
  \textit{refinement types} over the extracted type information to reduce false
  alarms.  \inred{TODO: explanation of refinement types.} We evaluated $\tool$
  with \inred{XXX different versions of ECMAScript in the official GitHub
  repository between 2018 June and 2021 March.} Among \inred{XXX} known
  specification errors, our tool detected \inred{XXX} errors with \inred{XXX}
  false alarms.  Moreover, $\tool$ detected \inred{X} new specification errors
  in the draft of next release of ECMAScript (ES12, 2021).
\end{abstract}
